StarCraft Bots and Competitions

### 2014-08-22 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
Added files to start working on the ECGG papers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Title
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{RTS AI Problems and Techniques
%\thanks{Supported by ...}
}

\author{Santiago~Onta\~{n}\'{o}n\inst{1} \and 
		Gabriel~Synnaeve\inst{2} \and
		Alberto~Uriarte\inst{1} \and
		Florian~Richoux\inst{3} \and
		David~Churchill\inst{4} \and
		Mike~Preuss\inst{5}
		}

\institute{
	Computer Science Department at Drexel University, Philadelphia, PA, USA. \\
	\email{\{santi,albertouri\}@cs.drexel.edu}
\and
	Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm, Paris, France. \\
	\email{gabriel.synnaeve@gmail.com}
\and
	Nantes Atlantic Computer Science Laboratory (LINA) of the Universit{\'e} de Nantes, France. \\
	\email{florian.richoux@univ-nantes.fr}
\and
	Computing Science Department of the University of Alberta, Edmonton, Canada. \\
	\email{cdavid@cs.ualberta.ca}
\and
	Department of Computer Science of Technische Universit{\"a}t Dortmund, Germany.
	\email{mike.preuss@cs.tu-dortmund.de}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Title
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{StarCraft Bots and Competitions
%\thanks{Supported by ...}
}

\author{David~Churchill\inst{1} \and
		Mike~Preuss\inst{2}		
		Florian~Richoux\inst{3} \and
		Gabriel~Synnaeve\inst{4} \and
		Alberto~Uriarte\inst{5} \and
		Santiago~Onta\~{n}\'{o}n\inst{5} \and 
		}

\institute{
	Computing Science Department of the University of Alberta, Edmonton, Canada. \\
	\email{cdavid@cs.ualberta.ca}
\and
	Department of Computer Science of Technische Universit{\"a}t Dortmund, Germany.
	\email{mike.preuss@cs.tu-dortmund.de}
\and
	Nantes Atlantic Computer Science Laboratory (LINA) of the Universit{\'e} de Nantes, France. \\
	\email{florian.richoux@univ-nantes.fr}
\and
	Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm, Paris, France. \\
	\email{gabriel.synnaeve@gmail.com}
\and
	Computer Science Department at Drexel University, Philadelphia, PA, USA. \\
	\email{\{santi,albertouri\}@cs.drexel.edu}
}
